Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-14 man/tables/t_sampled_plots.Rmd
update table

---
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: ../template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

colnames (t1) <- c("Site", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "Prec. (mm)", "Temp (&deg; C)",
                   "# trees (# cores)", "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)", "SRD")

>>>>

---
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

colnames (t1) <- c("Site", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "Prec. (mm)", "Temp. (&deg; C)",
                   "# trees (# cores)", "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)", "SRD")
